Fail Faster

### 2025-03-04 paper/paper.tex
blah

\subsubsection{Weighted unions}
% \subsubsection{Function call overhead}
\subsubsection{Boxed integers}

@@

\subsection{Comparing Generators}
\subsubsection{Existing Approaches}
\subsubsection{Equality up to Program Equality}
\subsubsection{Effect Ordering}
\subsubsection{PBT for PBT}
\subsubsection{Does maintaining program equality in \name\ affect performance?}
\section{Evaluation}
\subsubsection{Implementation}
\subsection{Benchmarking speed \& resource usage}
\subsection{Impact on bug-finding ability}
\section{Conclusion \& Future Work}
%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{bib}

>>>>

\subsubsection{Expensive Combinators}
\jwc{Many combinators like \texttt{union} and \texttt{weighted_union} needlessly allocate large data structures in the generation hot path.
Using a combination of staging and more careful algorithm design, we can avoid this overhead.
}
% \subsubsection{Function call overhead}
\subsubsection{Boxed integers}

@@

\subsection{Comparing Generators}

\jwc{NOTE: we should test generator speed across both languages, but speed -> bugfinding ability in only OCaml.}
\jwc{
  Baseline generators to test speed in both languages:
  \begin{itemize}
    \item Single int
    \item Pair of ints, constrained
    \item List of ints
  \end{itemize}
}

\subsubsection{Existing Approaches}
\subsubsection{Equality up to Program Equality}
\subsubsection{Effect Ordering}
\subsubsection{PBT for PBT}
\subsubsection{Does maintaining program equality in \name\ affect performance?}
\section{Evaluation}
\subsubsection{Implementation}
\subsection{Benchmarking speed \& resource usage}
\subsection{Impact on bug-finding ability}
\section{Conclusion \& Future Work}
%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{bib}
